A reproducible journal article with RMarkdown&#58; A  building science template with examples for beginners based on the Elsevier journal format

### 2019-02-13 Paper/Manuscript.Rmd
Change Figures to Images since latex produces separate directory for figures

**Graphical Abstract**  
```{r graphabs, message=FALSE}
#include a graphical abstract, without a caption
include_graphics(here("Paper","SupplementaryMaterial","Figures","Latex_logo.png"))

@@

```{r correlation, fig.width = 1, fig.cap = "Correlation. Source: XKCD, xkcd.com/552"}
include_graphics(here("Paper","SupplementaryMaterial","Figures","Correlation.png"), dpi= 500)
```

>>>>

**Graphical Abstract**  
```{r graphabs, message=FALSE}
#include a graphical abstract, without a caption
include_graphics(here("Paper","SupplementaryMaterial","Images","Latex_logo.png"))

@@

```{r correlation, fig.width = 1, fig.cap = "Correlation. Source: XKCD, xkcd.com/552"}
include_graphics(here("Paper","SupplementaryMaterial","Images","Correlation.png"), dpi= 500)
```
